How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2014-12-04 doc/draft_turtle.tex
generalization comparisons

% generalization
AUC values from model generalization, or estimating testing data set membership, does not indicate a clear ``best'' classification scheme (Fig. \ref{fig:gen_hist}). While the scheme with two species has the greatest AUC point estimate for each modeling approach, this scheme is not significantly greater from any other except in some limited cases (e.g. LDA).

>>>>

% generalization
AUC values from model generalization, or estimating testing data set membership, does not indicate a clear ``best'' classification scheme (Fig. \ref{fig:gen_hist}). While the scheme with two species has the greatest AUC point estimate for each modeling approach, this scheme is not significantly greater from any other except in some limited cases (e.g. LDA, Table \ref{tab:gen_tests}).

\begin{table}
  \include{rf_dif}
    %
  \include{mm_dif}
    %
  \include{ll_dif}
  \caption{Results of bootstrap comparisons between the scheme with the highest mean AUC value and all other schemes. An asterix indicates the best scheme. This was done for each of the three modeling techniques included in this study. Probabilities are the percent of comparisons that are greater than the observed difference in means.}
  \label{tab:gen_tests}
\end{table}
